<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-10-26 MainAnalysis.Rmd
Everything but 2comp plots and make_joint_sigma_plot working

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_05092022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_05092022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

pk_data_flat <- pk_output_flat_05092022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
  filter(Species != "hamster")

raw_data_flat <- dplyr::select(raw_flat_05092022, -c("A")) %>% 
  filter(Species != "hamster")

@@

# cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
# 
# cp_df <- cp_df %>% group_by(Species.x, 
#                             Compound,
#                             CAS,
#                             type) %>%
#   mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))

### here is where you save the Rdata file
save(cp_df, file = paste(figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
```

pk_data <- cp_df_05092022

# data <- cp_df_12212021
# data <- cp_df_03012022
data <- cp_df_04282022

data <- cp_df_04282022

@@

### all the raw data for each model SHOULD be the same
# so only need to use one
data <- as.data.table(raw_1comp_05092022)

@@

### combine data.tables back into one large data.set
cvt_variability_df_05092022 <- do.call(rbind, data.list)

### SAVE the data
save(cvt_variability_df_05092022, file = "figures_rdata/cvt_variability_df_05092022.Rdata")
```

@@

data <- cvt_variability_df_05092022
# data <- cvt_variability_df_12212021

@@

# pk_data <- cp_df_03012022
pk_data <- cp_df_05092022

cvt_data <- cvt_variability_df_05092022

@@

# pk_data <- cp_df_03012022
pk_data <- cp_df_04282022

cvt_data <- cvt_variability_df_04282022

@@

data <- raw_1comp_04282022

@@

data1 <- as.data.table(pk_output_1comp_04282022 %>%
                         filter(param.value.type == "Fitted geometric mean"))

data2 <- as.data.table(pk_output_2comp_04282022 %>%
                         filter(param.value.type == "Fitted geometric mean"))

@@

split_list_1 <- split(data1, data1$Compound)
rep_sigma_1 <- lapply(split_list_1, find_rep_sigma)
data1 <- do.call(rbind, rep_sigma_1)
data1 <- subset(data1, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data1$Data.Analyzed[data1$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data1 <- data1 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data1 <- data1 %>% filter(sigma_id != "sigma2.14")
data1$`Joint Analysis` <- as.numeric(data1$`Joint Analysis`)
data1$`Ind Analysis` <- as.numeric(data1$`Ind Analysis`)
data1$model <- "1-Compartment"

split_list_2 <- split(data2, data2$Compound)
rep_sigma_2 <- lapply(split_list_2, find_rep_sigma)
data2 <- do.call(rbind, rep_sigma_2)
data2 <- subset(data2, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data2$Data.Analyzed[data2$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data2 <- data2 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data2 <- data2 %>% filter(sigma_id != "sigma2.14")
data2$`Joint Analysis` <- as.numeric(data2$`Joint Analysis`)
data2$`Ind Analysis` <- as.numeric(data2$`Ind Analysis`)
data2$model <- "2-Compartment"

data <- rbind(data1, data2)

@@

raw_data1 <- raw_1comp_04282022

@@

pk_data1 <- pk_output_1comp_04282022 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

raw_data1 <- dplyr::select(raw_data1, -c("X",
                                         "kelim",
                                         "Vdist",
                                         "Fgutabs",
                                         "kgutabs"))

@@

raw_data2 <- raw_2comp_04282022

pk_data2 <- pk_output_2comp_04282022 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

pk_data1 <- pk_output_1comp_04282022 
# pk_data1 <- pk_output_1comp_12212021

pk_data2 <- pk_output_2comp_04282022 
# pk_data2 <- pk_output_2comp_12212021

@@

pk_data1 <- as.data.table(pk_output_1comp_04282022)
pk_data2 <- as.data.table(pk_output_2comp_04282022)

@@

  this.compound.data <- pk_all[Compound == this.compound]

@@

pk_data1 <- pk_output_1comp_04282022

pk_data2 <- pk_output_2comp_04282022

pk_data_flat <- pk_output_flat_04282022 %>%
  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")

@@

pk_data1 <- pk_output_1comp_05092022
# pk_data1 <- pk_output_1comp_04282022

>>>>

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

pk_data_flat <- pk_output_flat %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
  filter(Species != "hamster")

raw_data_flat <- dplyr::select(raw_flat, -c("A")) %>% 
  filter(Species != "hamster")

@@

cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value

cp_df <- cp_df %>% group_by(Species.x, 
                           Compound,
                           CAS,
                           type) %>%
 mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))

### here is where you save the Rdata file
save(cp_df, file = paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
```

@@

### all the raw data for each model SHOULD be the same
# so only need to use one
data <- as.data.table(raw_1comp)

@@

### combine data.tables back into one large data.set
cvt_variability_df <- do.call(rbind, data.list)

### SAVE the data
save(cvt_variability_df, file = paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))
```

pk_data <- cp_df

# data <- cp_df_12212021
# data <- cp_df_03012022
data <- cp_df

data <- cp_df

@@

data <- cvt_variability_df
# data <- cvt_variability_df_12212021

@@

# pk_data <- cp_df_03012022
pk_data <- cp_df

cvt_data <- cvt_variability_df

@@

# pk_data <- cp_df_03012022
pk_data <- cp_df

cvt_data <- cvt_variability_df

@@

data <- raw_1comp

@@

data1 <- as.data.table(pk_output_1comp %>%
                         filter(param.value.type == "Fitted geometric mean"))

data2 <- as.data.table(pk_output_2comp %>%
                         filter(param.value.type == "Fitted geometric mean"))

@@

split_list_1 <- split(data1, data1$Compound)
rep_sigma_1 <- lapply(split_list_1, find_rep_sigma)
data1 <- do.call(rbind, rep_sigma_1)
data1 <- subset(data1, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data1$Data.Analyzed[data1$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data1 <- data1 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data1 <- data1 %>% filter(sigma_id != "sigma2.14")
data1$`Joint Analysis` <- lapply(data1$`Joint Analysis`,as.numeric)
data1$`Ind Analysis` <- lapply(data1$`Ind Analysis`,as.numeric)
data1$model <- "1-Compartment"

split_list_2 <- split(data2, data2$Compound)
rep_sigma_2 <- lapply(split_list_2, find_rep_sigma)
data2 <- do.call(rbind, rep_sigma_2)
data2 <- subset(data2, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data2$Data.Analyzed[data2$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data2 <- data2 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data2 <- data2 %>% filter(sigma_id != "sigma2.14")
data2$`Joint Analysis` <- lapply(data2$`Joint Analysis`,as.numeric)
data2$`Ind Analysis` <- lapply(data2$`Ind Analysis`,as.numeric)
data2$model <- "2-Compartment"

data <- as.data.table(rbind(data1, data2))

@@

raw_data1 <- raw_1comp

@@

pk_data1 <- pk_output_1comp %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

raw_data1 <- dplyr::select(raw_data1, -c("kelim",
                                         "Vdist",
                                         "Fgutabs",
                                         "kgutabs"))

@@

raw_data2 <- raw_2comp

pk_data2 <- pk_output_2comp %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

pk_data1 <- pk_output_1comp
# pk_data1 <- pk_output_1comp_12212021

pk_data2 <- pk_output_2comp
# pk_data2 <- pk_output_2comp_12212021

@@

pk_data1 <- as.data.table(pk_output_1comp)
pk_data2 <- as.data.table(pk_output_2comp)

@@

  this.compound.data <- pk_all[Compound == this.compound]
  this.compound.data$AIC[is.na(this.compound.data$AIC)] <- Inf

@@

pk_data1 <- pk_output_1comp

pk_data2 <- pk_output_2comp

pk_data_flat <- pk_output_flat %>%
  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")

@@

pk_data1 <- pk_output_1comp
# pk_data1 <- pk_output_1comp_04282022
